Extracting Application and Menu Events from UI Tutorial Videos

### 2015-05-10 paper/main.tex
Modified filters for 1000 iterations

\documentclass[10pt]{article}
\usepackage[backend=bibtex,style=numeric]{biblatex}
%\usepackage{simplestyle}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{fullpage}

@@

This work seeks to use video processing and object recognition techniques as a technique to
mine the usability of an application.  Given the proliferation of video tutorials on using
different software, this provides new opportunities to assess what complex actions are frequently
performed by a variety of users.  We describe a technique for recognizing menus, detecting that an
item has been clicked in a menu, comparing this menu item to all other instances of that same item
by template matching, and then composing temporally close menu navigations into configuration tasks.
By working with a corpus of around 100 tutorials related to setting up the Eclipse environment for
programming tasks, we describe the configuration tasks that are performed the most often.  We
discuss how we can improve this workflow to improve the speed and accuracy of detection in the
future.

Our contributions include a small but effective dataset for evaluating the effectiveness of
detectors of UI menu-opening actions.

Recent research has focused on how to improve the use of video tutorials to help users learn
software ~\cite{matejka_ambient_2011}~\cite{pongnumkul_pause-and-play_2011}.  One strength of video
tutorials may be that users can directly observe expert use, which can serve as a strong learning
aid~\cite{shneiderman_direct_1983}.  Grossman \& Fitzmaurice showed benefits of short contextual
video clips.  Short, 10-25 second contextually available videos were effective to help users
accomplish task and retain what they learned than traditional text-based
tutorials~\cite{grossman_toolclips_2010}.

However, video tutorials have drawbacks: Navigation issues could lead to misunderstanding of
content~\cite{harrison_comparison_1995}.  Users may not be able to keep up with the pace of the
content~\cite{palmiter_evaluation_1991}.  Researchers working with longer, 2-3 minute task-oriented
tutorials found that users performed better with text tutorials than videos because users could not
work at the same pace as the video~\cite{grabler_generating_2009}.  In general, research on
instructional videos point shows a need to segmented videos to emphasize the steps of the task.

\textbf{Andrew: Make this have less of a strong focus on the value of video tutorials, and instead
talk about mining usability from online data sources, such as with CUTS}

\section{Related Work}

@@

Figures~\ref{fig:filters_all} and~\ref{fig:filters_nonoise} show visualizations of the 96 filters in
the first layer of AlexNet, each of which has dimension $55\times 55$.

\begin{figure}
\centering
  \begin{minipage}{.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_All}
  \caption{Visualization of filters from the network trained on all our image data.}
  \label{fig:filters_all}
  \end{minipage}\hfill
  \begin{minipage}{.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_NoNoise}
  \caption{Visualization of filters from the network trained on ``no noise'' image data.}
  \label{fig:filters_nonoise}
  \end{minipage}
\end{figure}

>>>>

\documentclass[10pt]{article}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{fullpage}

@@

In this project, we present two main contributions. First, we show that a standard neural network
following the AlexNet architecture with minimal tweaking can accurately recognize frames belonging
to a class of videos.  Second, we present a pipeline and procedure for detecting menus within a
video frame sequence. We then discuss how these two stages might be combined to enhance the process
of extracting useful information from videos.

\subsection{Motivation}

The proliferation of video tutorials on using different software raises new research questions on
how to improve their use to help users learn software~\cite{matejka_ambient_2011,
pongnumkul_pause-and-play_2011}.  One strength of video tutorials may be that users can directly
observe expert use, which can serve as a strong learning aid. Grossman \& Fitzmaurice showed
benefits of brief contextual video clips: short, 10-25 second contextually available videos were
effective to help users accomplish task and retain what they learned than traditional text-based
tutorials~\cite{grossman_toolclips_2010}. Unfortunately, video tutorials have drawbacks. Navigation
issues could lead to misunderstanding of content, and users may not be able to keep up with the pace
of instruction. Researchers working with longer, 2-3 minute task-oriented tutorials found that users
performed better with text tutorials than videos because users could not work at the same pace as
the video~\cite{grabler_generating_2009}.

In general, research on instructional videos point shows a need to segmented videos to emphasize the
steps of the task. One way to do that might be to develop techniques for detecting locations of
certain menu actions in the video, such as when the video shows its user clicking on a button in a
Photoshop video to create a blank image. Our goal, therefore, is to utilize computer vision
techniques to aid in this process.

\subsection{Related Work}

@@

Figures~\ref{fig:filters_all} and~\ref{fig:filters_nonoise} show visualizations of the 96 filters in
the first layer of AlexNet, each of which has dimension $55\times 55$. These were taken for the
model that had 1000 iterations of training.

\begin{figure}
\centering
  \begin{minipage}{.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_All1000}
  \caption{Visualization of filters from the network trained on all our image data.}
  \label{fig:filters_all}
  \end{minipage}\hfill
  \begin{minipage}{.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_NoNoise1000}
  \caption{Visualization of filters from the network trained on ``no noise'' image data.}
  \label{fig:filters_nonoise}
  \end{minipage}
\end{figure}
